---
title: "Lab 13: Multiple Regression"
output:
  pdf_document:
    fig_height: 2.8
    fig_width: 6
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
header-includes:
  - \usepackage{booktabs}
  - \usepackage{vwcol}
geometry: margin=0.5in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE)
library(ggplot2)
library(readr)
library(dplyr)
library(gridExtra)
library(GGally)
options(width = 100)
```

## Pace of Life (Adapted from Sleuth3 Exercise 9.14)

We have observations on indicators of pace of life from 36 different metropolitan regions of different sizes throughout the United States:

* `Bank`: bank clerk speed
* `Walk`: pedestrian walking speed
* `Talk`: postal clerk talking speed
* `Heart`: age adjusted death rate due to heart disease

```{r}
pace <- read_csv("http://www.evanlray.com/data/sleuth3/ex0914_pace_of_life.csv")
```

Let's model the relationship between the death rate due to heart disease (our response variable) and the other indicators of pace of life.

#### 1. Make a pairs plot of the data.

```{r}
ggpairs(pace)
```

#### 2. Based on your pairs plot, perform an initial check of the conditions of linearity, equal variance, and no outliers/high leverage observations.  Do you see any potential causes for concern?



#### 3. Fit a model that has Heart as the response and the other three variables in the data set as explanatory variables.  Print a summary of your model fit.  Is there any indication of associations between the variables in the model and the rate of deaths due to heart disease?

```{r}
lm_fit <- lm(Heart ~ Bank + Walk + Talk, data = pace)
summary(lm_fit)
```

#### 4. Make plots showing the leverage, studentized residual, and Cook's distance for each observation.  Do these diagnostics suggest that any observations are worth investigating further?

```{r}
pace <- pace %>%
  mutate(
    obs_index = row_number(),
    h = hatvalues(lm_fit),
    studres = rstudent(lm_fit),
    D = cooks.distance(lm_fit)
  )

ggplot(data = pace, mapping = aes(x = obs_index, y = h)) +
  geom_hline(yintercept = 2*4/ nrow(pace))+
  geom_point()

ggplot(data = pace, mapping = aes(x = obs_index, y = studres)) +
  geom_point()

ggplot(data = pace, mapping = aes(x = obs_index, y = D)) +
  geom_point()
```

The plot of leverage indicates that we should investigate observations 35 and 36 to see if they are affecting our inferences too much.

#### 6. Make scatter plots of each quantitative explanatory variable vs. the response, highlighting any observations you identified above as being worth further attention.

```{r}
obs_to_investigate <- c(35, 36)

pace <- pace %>%
  mutate(
    suspicious = row_number() %in% obs_to_investigate
  )

ggplot(data = pace, mapping = aes(x = Bank, y = Heart, color = suspicious)) +
  geom_point() +
  geom_label(data = pace %>% filter(suspicious), mapping = aes(label = obs_index))

ggplot(data = pace, mapping = aes(x = Walk, y = Heart, color = suspicious)) +
  geom_point() +
  geom_label(data = pace %>% filter(suspicious), mapping = aes(label = obs_index))

ggplot(data = pace, mapping = aes(x = Talk, y = Heart, color = suspicious)) +
  geom_point() +
  geom_label(data = pace %>% filter(suspicious), mapping = aes(label = obs_index))
```

#### 7. Create a version of the data set that does not include any suspect observations.  Fit the model again, without those suspect observations.  Print a summary of your model fit.

```{r}
pace2 <- pace %>%
  filter(
    !suspicious
  )

lm_fit2 <- lm(Heart ~ Bank + Walk + Talk, data = pace2)
summary(lm_fit2)
```

#### 8. How would you sum up what you have learned about the associations between each of the explanatory variables and the response based on this analysis?



#### 9. What is the interpretation of the coefficient estimate for "Walk" in your model fit?



